---
title: "TSA project"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}


setwd("/Users/zhanfengzhao/Downloads/2020Spring/TSA/project")
df=read.csv("export_dataframe.csv")

library(fpp2)
library(forecast)
library(ggplot2)
library(urca)

```

## Define questions

1. Predict weekly sales
2. Which factors have biggest impact on weekly sales? 

## Data description

| Variable Description |
|------|
|Temperature|
|Fuel price|
|CPI| 
|Unemployment rate|
|IsHoliday|

```{r weekly_sales}
head(df)
summary(df)
dim(df)

```

### Data cleaning

Python steps

### Data limitation

1. Small sample
2. Select one store to perform the analysis


```{r weekly_sales1}
store1<-subset(df, Store==1)
dim(store1)
```
## Time plots
```{r weekly_sales2, echo=FALSE}

y = ts(data=store1$Weekly_Sales/1000000, frequency = 52, start = c(2010,2),end=c(2012,11))

autoplot(y)+
  ggtitle("Weekly Sales 2010/2 - 2012/11")+
  xlab("Year")+ylab("$ millions")


```

```{r weekly_sales3, echo=FALSE}

ggAcf(y)


```

```{r weekly_sales3, echo=FALSE}

ggseasonplot(y, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("$ million") +
  ggtitle("Seasonal plot: Weekly Sales 2010/2 - 2012/11")


```

## Time series pattern

Obvious seasonality. r1 and r52 are higher than for the other lags, this is due to the seasonal pattern in the data.

## Forecast analysis

### Simple forecast methods

```{r weekly_sales5, echo=FALSE}

## I removed naive method since there is an obvious seasonality pattern. 


autoplot(y) +
  autolayer(meanf(y, h=52),
    series="Mean", PI=FALSE) +
  autolayer(snaive(y, h=52),
    series="Seasonal naïve", PI=FALSE) +
  autolayer(rwf(y, h=52, drift=TRUE), 
    series="Drift", PI=FALSE)+   
  ggtitle("Forecasts for weekly_sales") +
  xlab("Year") + ylab("$ Millions") +
  guides(colour=guide_legend(title="Forecast"))


```

Seasonal naive method has the lowest RMSE, it is the best fit model under simple forecast methods.

```{r weekly_sales6, echo=FALSE}

fit1 <- meanf(y, h=52)
fit2 <- snaive(y, h=52)
fit3 <- rwf(y, h=52, drift=TRUE)
accuracy(fit1)
accuracy(fit2)
accuracy(fit3)

```

## ETS

decompose time series

```{r weekly_sales7, echo=FALSE}

mstl(y) %>% autoplot

```



### ETS model with seasonality

```{r weekly_sales9, echo=FALSE}


fit4=stlf(y,method="ets",allow.multiplicative.trend=TRUE)

summary(fit4)
autoplot(y) +
  autolayer(forecast(stlf(y,method="ets",allow.multiplicative.trend=TRUE), h=52), PI=FALSE, series="ETS")

accuracy(fit4)

```

## SARIMA 

Step 1 - check stationarity
If a time series has a trend or seasonality component, it must be made stationary before we can use ARIMA to forecast. 

Step 2 - difference
If the time series is not stationary, it needs to be stationarized through differencing. According to the summary, we cannot reject the null hypothersis at 5% significant level. Therefore the data is stationary. 

```{r weekly_sales10, echo=FALSE}

y %>% diff(lag=52) %>% ggtsdisplay()

fit5<-auto.arima(y, stepwise=FALSE,approximation=FALSE)
summary(fit5)

autoplot(y) +
  autolayer(forecast(fit5, h=52), PI=FALSE, series="Seasonal Arima")




```

## Linear Rregression models

### Correlations between varivales

```{r weekly_sales11, echo=FALSE}

install.packages('corrr')
library(corrr)
store1$IsHoliday<- as.numeric(store1$IsHoliday) - 1
correlate(store1[c(3:8)])

```


```{r weekly_sales11, echo=FALSE}

df3<- subset(store1,
select=c(Temperature, Fuel_Price, CPI, Unemployment, IsHoliday, Weekly_Sales))

df3%>%
  as.data.frame %>%
  GGally::ggpairs()

```


## Dynamic regression 
```{r weekly_sales13, echo=FALSE}
store1<-subset(df, Store==1)
store1$IsHoliday<- as.numeric(store1$IsHoliday) - 1
y2 = ts(data=store1, frequency = 52, start = c(2010,2),end=c(2012,10))
fit1 <- Arima(y2[,"Weekly_Sales"]/1000000, xreg = y2[,c("Temperature","Fuel_Price","CPI","Unemployment")],
                   order = c(0,0,0),seasonal = c(0,1,0))
summary(fit1)
```
```{r}
checkresiduals(fit1)
```


